Supplementary Figures

### 2024-04-18 02b_supplementary_plots.Rmd
update title
check paths

---
title: "supplementary plots"
output: html_document
date: "2024-02-09"
---

@@

# Open dataset-------------
# start with lake temperatures
temperature_scores <- arrow::open_dataset("./scores_2023") |>
  dplyr::filter(!(model_id %in% c('flareGOTM','flareGOTM_noDA', 'flare_ler', 'flare_ler_baseline') &
                  site_id == 'TOOK')) |> 
  filter(site_id %in% lake_sites,
         model_id %in% model_meta$model_id,
         variable == 'temperature') |>
  collect()

# Calculate skill scores ------------
temperature_climatology <- arrow::open_dataset("./scores_2023") |>
  filter(model_id == 'climatology', 
         site_id %in% lake_sites,
         variable == 'temperature') |>
  collect() |> 
  select(reference_datetime, datetime, crps, logs, site_id, model_id) |> 
  arrange(reference_datetime, datetime, site_id) |> 
  pivot_wider(values_from = c(crps, logs),
              names_from = model_id)

@@

```{r}
baseline_forecasts <- arrow::open_dataset("scores_2023") |>
  filter(site_id %in% lake_sites,
         model_id %in% c('persistenceRW', 'climatology')) |>
  collect()

>>>>

---
title: "Supplementary Figures"
output: html_document
date: "2024-02-09"
---

@@

# Open dataset-------------
# start with lake temperatures
temperature_scores <- arrow::open_dataset("./scores") |>
  dplyr::filter(!(model_id %in% c('flareGOTM','flareGOTM_noDA', 'flare_ler', 'flare_ler_baseline') &
                  site_id == 'TOOK')) |> 
  filter(site_id %in% lake_sites,
         model_id %in% model_meta$model_id,
         variable == 'temperature') |>
  collect()

# Calculate skill scores ------------
temperature_climatology <- arrow::open_dataset("./scores") |>
  filter(model_id == 'climatology', 
         site_id %in% lake_sites,
         variable == 'temperature') |>
  collect() |> 
  select(reference_datetime, datetime, crps, logs, site_id, model_id) |> 
  arrange(reference_datetime, datetime, site_id) |> 
  pivot_wider(values_from = c(crps, logs),
              names_from = model_id)

@@

```{r}
baseline_forecasts <- arrow::open_dataset("scores") |>
  filter(site_id %in% lake_sites,
         model_id %in% c('persistenceRW', 'climatology')) |>
  collect()
